Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-18 doc/manuscript/ESSDmanuscript.Rmd
start recommendations table

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#Tables
table_pools =1
table_variables =2

@@

We recommend that, unless they have some specific reason to do otherwise, researchers calculate and report the values according to IPCC standards:

  - adopt common standards for variables like min diameter of deadwood, select soil sampling increments to include a cutoff at 30.

  - report 95% CIs, SE, or STD and n

  - report C variables in article text, table, or SI table. EFDB cannot accept data digitized from figures

  - present calculations of all variables that would be useful to IPCC. EFDB requires that data in the database be presented in the original article, and as such cannot accept subsequent calculations. For example, if aboveground biomass and total biomass are presented, but root biomass is not presented, root biomass cannot be subsequently calculated and sent to EFDB. Similarly, fine and coarse root biomass can't be summed; soil carbon can't be summed across depth increments, etc.

@@

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#Tables
table_pools =1
table_variables =2
table_recommendations = 3

@@

We recommend that, unless they have some specific reason to do otherwise, researchers calculate and report the values according to IPCC standards (`r table_recommendations`).

@@

```{r table_recommendations, eval = TRUE, echo=FALSE, warning=FALSE}
recommendations_table <- read.csv("figures_tables/recommendations.csv")
names(recommendations_table) <- stringr::str_replace_all(names(recommendations_table), "\\.", " ")

library(knitr)
library(kableExtra)
knitr::kable(recommendations_table, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{Recommended best practices for reporting forest C estimates of value to national greenhouse gas inventories under IPCC guidance. } ....") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)
```

### 2022-04-18 doc/manuscript/ESSDmanuscript.tex
start recommendations table

We recommend that, unless they have some specific reason to do
otherwise, researchers calculate and report the values according to IPCC
standards:

\begin{itemize}
\item
  adopt common standards for variables like min diameter of deadwood,
  select soil sampling increments to include a cutoff at 30.
\item
  report 95\% CIs, SE, or STD and n
\item
  report C variables in article text, table, or SI table. EFDB cannot
  accept data digitized from figures
\item
  present calculations of all variables that would be useful to IPCC.
  EFDB requires that data in the database be presented in the original
  article, and as such cannot accept subsequent calculations. For
  example, if aboveground biomass and total biomass are presented, but
  root biomass is not presented, root biomass cannot be subsequently
  calculated and sent to EFDB. Similarly, fine and coarse root biomass
  can't be summed; soil carbon can't be summed across depth increments,
  etc.
\end{itemize}

@@

>>>>

We recommend that, unless they have some specific reason to do
otherwise, researchers calculate and report the values according to IPCC
standards (3).

@@

\caption{\label{tab:table_recommendations}\textbf{Recommended best practices for reporting forest C estimates of value to national greenhouse gas inventories under IPCC guidance. } ....}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{criteria} & \textbf{recommendation} & \textbf{rationale}\\
\hline
variables to include & When possible, calculate and present all relevant variables that can be readily caluclated based on available data. & Estimates of relevant variables are not always calcualted.\\
\hline
forest census methods & Census stems down to the smallest diameter feasible. & IPCC biomass pool definition includes all living vegetation\\
\hline
 & taxa to include: & IPCC biomass pool definition includes all living vegetation\\
\hline
dead organic matter sampling & include damage estimates on standing dead trees & \\
\hline
 & adopt IPCC recommendations for min diameter of deadwood & \\
\hline
belowground sampling & Select soil sampling increments to include a cutoff at 30 cm depth. & \\
\hline
reporting variiables & Present each variable individually, as opposed to requiring that variables of interest be calculated from related variables. & EFDB requires that values in the database be presented in the original article, and cannot accept subsequent calculations.\\
\hline
reporting estimates & Report all relevant values in tables, text, or supplementary tables/ data files, as opposed to in figures only. & EFDB does not acceptvalues digitized from figures.\\
\hline
reporting confidence intervals & Report 95\% confidence intervals, standard error, or standard deviation and sample size. & EFDB requires confidence invervals, when possible.\\
\hline
\end{tabu}
\end{table}
